### 2022-12-04 output/article.tex
feat: generalize maclaurin series to taylor series

We shall ponder the following:
\begin{equation}
1 
\end{equation}
Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

The following is worth a closer look:
\begin{equation}
x ^{2 } 
\end{equation}
It is now obvious, that the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

We shall ponder the following:
\begin{equation}
x - 2 
\end{equation}
Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
\begin{equation}
1 - 0 
\end{equation}

We shall ponder the following:
\begin{equation}
x + 1 
\end{equation}
As you can see, the derivative of this is equal to
\begin{equation}
1 + 0 
\end{equation}

Let us take a look at this:
\begin{equation}
2 
\end{equation}
Obviously, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

The object of our ultimate interest is the following:
\begin{equation}
\sin x 
\end{equation}
Obviously, the derivative of this is equal to
\begin{equation}
\cos x \cdot 1 
\end{equation}

@@

\newpage
\section{Taylor series}
Let us find the Taylor series at $x = 0$ of the following function:
\begin{equation}
\left( x + 1 \right) ^{\frac{\sin x }{2 } } \cdot \left( \arctan \sqrt {x ^{2 } + 1 } \right) ^{x - 2 } 
\end{equation}

The following is worth a closer look:
\begin{equation}
1 
\end{equation}
It can be easily proved, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We are going to study the following:
\begin{equation}
x ^{2 } 
\end{equation}
Clearly, the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

We shall ponder the following:
\begin{equation}
x - 2 
\end{equation}
Unsurprisingly, the derivative of this is equal to
\begin{equation}
1 - 0 
\end{equation}

The object of our ultimate interest is the following:
\begin{equation}
x + 1 
\end{equation}
It can be easily proved, that the derivative of this is equal to
\begin{equation}
1 + 0 
\end{equation}

We will take a closer look at this:
\begin{equation}
2 
\end{equation}
It is now obvious, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We are going to study the following:
\begin{equation}
\sin x 
\end{equation}
It can be easily proved, that the derivative of this is equal to
\begin{equation}
\cos x \cdot 1 
\end{equation}

One shall regard the object in question with utmost interest:
\begin{equation}
1 
\end{equation}
It can be easily proved, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We will take a closer look at this:
\begin{equation}
x ^{2 } 
\end{equation}
It can be easily proved, that the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

The following is worth a closer look:
\begin{equation}
2 \cdot x 
\end{equation}
As you can see, the derivative of this is equal to
\begin{equation}
0 \cdot x + 2 \cdot 1 
\end{equation}

The following is worth a closer look:
\begin{equation}
1 
\end{equation}
Clearly, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

The object of our ultimate interest is the following:
\begin{equation}
x ^{2 } 
\end{equation}
It can be easily proved, that the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
\begin{equation}
2 
\end{equation}
It can be easily proved, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
\begin{equation}
1 
\end{equation}
It is now obvious, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

Consider the following:
\begin{equation}
1 
\end{equation}
Clearly, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

The object of our ultimate interest is the following:
\begin{equation}
x ^{2 } 
\end{equation}
Unsurprisingly, the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

The object of our ultimate interest is the following:
\begin{equation}
1 
\end{equation}
It is now obvious, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

The following is worth a closer look:
\begin{equation}
1 
\end{equation}
As you can see, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
\begin{equation}
x - 2 
\end{equation}
Obviously, the derivative of this is equal to
\begin{equation}
1 - 0 
\end{equation}

Consider the following:
\begin{equation}
1 
\end{equation}
Trivially, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We shall ponder the following:
\begin{equation}
x ^{2 } 
\end{equation}
It can be easily proved, that the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

@@

One shall regard the object in question with utmost interest:
\begin{equation}
x ^{2 } 
\end{equation}
Obviously, the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

We are going to study the following:
\begin{equation}
x - 2 
\end{equation}
It can be easily proved, that the derivative of this is equal to
\begin{equation}
1 - 0 
\end{equation}

We will take a closer look at this:
\begin{equation}
2 
\end{equation}
Clearly, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

Consider the following:
\begin{equation}
\sin x 
\end{equation}
Unsurprisingly, the derivative of this is equal to
\begin{equation}
\cos x \cdot 1 
\end{equation}

We shall ponder the following:
\begin{equation}
x ^{2 } 
\end{equation}
Trivially, the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

We will take a closer look at this:
\begin{equation}
x - 2 
\end{equation}
It can be easily proved, that the derivative of this is equal to
\begin{equation}
1 - 0 
\end{equation}

Let us take a look at this:
\begin{equation}
x + 1 
\end{equation}
Clearly, the derivative of this is equal to
\begin{equation}
1 + 0 
\end{equation}

We are going to study the following:
\begin{equation}
1 
\end{equation}
Trivially, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
\begin{equation}
2 
\end{equation}
It is now obvious, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We will take a closer look at this:
\begin{equation}
\sin x 
\end{equation}
Trivially, the derivative of this is equal to
\begin{equation}
\cos x \cdot 1 
\end{equation}

We shall ponder the following:
\begin{equation}
x + 1 
\end{equation}
It is now obvious, that the derivative of this is equal to
\begin{equation}
1 + 0 
\end{equation}

Let us take a look at this:
\begin{equation}
4 
\end{equation}
As you can see, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
\begin{equation}
2 
\end{equation}
It can be easily proved, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

Let us take a look at this:
\begin{equation}
\cos x 
\end{equation}
As you can see, the derivative of this is equal to
\begin{equation}
-\sin x \cdot 1 
\end{equation}

The following is worth a closer look:
\begin{equation}
x + 1 
\end{equation}
As you can see, the derivative of this is equal to
\begin{equation}
1 + 0 
\end{equation}

Consider the following:
\begin{equation}
\sin x 
\end{equation}
Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
\begin{equation}
\cos x \cdot 1 
\end{equation}

One shall regard the object in question with utmost interest:
\begin{equation}
1 
\end{equation}
Trivially, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

The following is worth a closer look:
\begin{equation}
x ^{2 } 
\end{equation}
Unsurprisingly, the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

The following is worth a closer look:
\begin{equation}
2 \cdot x 
\end{equation}
Trivially, the derivative of this is equal to
\begin{equation}
0 \cdot x + 2 \cdot 1 
\end{equation}

One shall regard the object in question with utmost interest:
\begin{equation}
2 
\end{equation}
Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

Let us take a look at this:
\begin{equation}
1 
\end{equation}
Obviously, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

Let us take a look at this:
\begin{equation}
1 
\end{equation}
Obviously, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We are going to study the following:
\begin{equation}
x ^{2 } 
\end{equation}
Clearly, the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

We will take a closer look at this:
\begin{equation}
1 
\end{equation}
Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

Let us take a look at this:
\begin{equation}
1 
\end{equation}
As you can see, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We shall ponder the following:
\begin{equation}
2 \cdot x 
\end{equation}
It can be easily proved, that the derivative of this is equal to
\begin{equation}
0 \cdot x + 2 \cdot 1 
\end{equation}

The object of our ultimate interest is the following:
\begin{equation}
1 
\end{equation}
Obviously, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

One shall regard the object in question with utmost interest:
\begin{equation}
x ^{2 } 
\end{equation}
Trivially, the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
\begin{equation}
2 
\end{equation}
As you can see, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We will take a closer look at this:
\begin{equation}
1 
\end{equation}
Obviously, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

The following is worth a closer look:
\begin{equation}
1 
\end{equation}
It can be easily proved, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

One shall regard the object in question with utmost interest:
\begin{equation}
x ^{2 } 
\end{equation}
As you can see, the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

The following is worth a closer look:
\begin{equation}
1 
\end{equation}
As you can see, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

The following is worth a closer look:
\begin{equation}
1 
\end{equation}
It is now obvious, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We are going to study the following:
\begin{equation}
1 
\end{equation}
As you can see, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We will take a closer look at this:
\begin{equation}
x ^{2 } 
\end{equation}
Trivially, the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

We will take a closer look at this:
\begin{equation}
2 \cdot x 
\end{equation}
It can be easily proved, that the derivative of this is equal to
\begin{equation}
0 \cdot x + 2 \cdot 1 
\end{equation}

We shall ponder the following:
\begin{equation}
1 
\end{equation}
Clearly, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
\begin{equation}
x ^{2 } 
\end{equation}
It is now obvious, that the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

The following is worth a closer look:
\begin{equation}
2 
\end{equation}
It can be easily proved, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

Consider the following:
\begin{equation}
1 
\end{equation}
Unsurprisingly, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

The following is worth a closer look:
\begin{equation}
x ^{2 } 
\end{equation}
Unsurprisingly, the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

We shall ponder the following:
\begin{equation}
1 
\end{equation}
Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

The object of our ultimate interest is the following:
\begin{equation}
2 \cdot x 
\end{equation}
As you can see, the derivative of this is equal to
\begin{equation}
0 \cdot x + 2 \cdot 1 
\end{equation}

We are going to study the following:
\begin{equation}
x ^{2 } 
\end{equation}
It is now obvious, that the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

The following is worth a closer look:
\begin{equation}
2 
\end{equation}
Clearly, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

Consider the following:
\begin{equation}
1 
\end{equation}
Clearly, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

Consider the following:
\begin{equation}
1 
\end{equation}
It is now obvious, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

Let us take a look at this:
\begin{equation}
x ^{2 } 
\end{equation}
Clearly, the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
\begin{equation}
2 
\end{equation}
Trivially, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
\begin{equation}
2 \cdot x 
\end{equation}
As you can see, the derivative of this is equal to
\begin{equation}
0 \cdot x + 2 \cdot 1 
\end{equation}

We are going to study the following:
\begin{equation}
1 
\end{equation}
As you can see, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

Consider the following:
\begin{equation}
x ^{2 } 
\end{equation}
Obviously, the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

We are going to study the following:
\begin{equation}
2 
\end{equation}
As you can see, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
\begin{equation}
2 \cdot x 
\end{equation}
It is now obvious, that the derivative of this is equal to
\begin{equation}
0 \cdot x + 2 \cdot 1 
\end{equation}

Let us take a look at this:
\begin{equation}
1 
\end{equation}
Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

One shall regard the object in question with utmost interest:
\begin{equation}
x ^{2 } 
\end{equation}
Obviously, the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

Consider the following:
\begin{equation}
2 
\end{equation}
As you can see, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

One shall regard the object in question with utmost interest:
\begin{equation}
2 
\end{equation}
It can be easily proved, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

The following is worth a closer look:
\begin{equation}
1 
\end{equation}
Obviously, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We shall ponder the following:
\begin{equation}
x ^{2 } 
\end{equation}
Unsurprisingly, the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
\begin{equation}
1 
\end{equation}
As you can see, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

@@

The following is worth a closer look:
\begin{equation}
x ^{2 } 
\end{equation}
Unsurprisingly, the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

We shall ponder the following:
\begin{equation}
1 
\end{equation}
Obviously, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

Consider the following:
\begin{equation}
1 
\end{equation}
Clearly, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

The following is worth a closer look:
\begin{equation}
x - 2 
\end{equation}
As you can see, the derivative of this is equal to
\begin{equation}
1 - 0 
\end{equation}

We are going to study the following:
\begin{equation}
1 
\end{equation}
Unsurprisingly, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We shall ponder the following:
\begin{equation}
x ^{2 } 
\end{equation}
As you can see, the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
\begin{equation}
2 \cdot x 
\end{equation}
As you can see, the derivative of this is equal to
\begin{equation}
0 \cdot x + 2 \cdot 1 
\end{equation}

We will take a closer look at this:
\begin{equation}
1 
\end{equation}
It can be easily proved, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

One shall regard the object in question with utmost interest:
\begin{equation}
x ^{2 } 
\end{equation}
Unsurprisingly, the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

One shall regard the object in question with utmost interest:
\begin{equation}
2 
\end{equation}
Obviously, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

The object of our ultimate interest is the following:
\begin{equation}
1 
\end{equation}
It can be easily proved, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
\begin{equation}
x ^{2 } 
\end{equation}
Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

We shall ponder the following:
\begin{equation}
2 \cdot x 
\end{equation}
It is now obvious, that the derivative of this is equal to
\begin{equation}
0 \cdot x + 2 \cdot 1 
\end{equation}

The object of our ultimate interest is the following:
\begin{equation}
1 
\end{equation}
It is now obvious, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

One shall regard the object in question with utmost interest:
\begin{equation}
2 
\end{equation}
It can be easily proved, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

One shall regard the object in question with utmost interest:
\begin{equation}
1 
\end{equation}
Trivially, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

Consider the following:
\begin{equation}
1 
\end{equation}
Unsurprisingly, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

One shall regard the object in question with utmost interest:
\begin{equation}
x ^{2 } 
\end{equation}
Clearly, the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

Consider the following:
\begin{equation}
1 
\end{equation}
Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

@@

The following is worth a closer look:
\begin{equation}
x ^{2 } 
\end{equation}
Clearly, the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

The object of our ultimate interest is the following:
\begin{equation}
1 
\end{equation}
Obviously, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We are going to study the following:
\begin{equation}
1 
\end{equation}
Trivially, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

Consider the following:
\begin{equation}
x ^{2 } 
\end{equation}
As you can see, the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

The following is worth a closer look:
\begin{equation}
x - 2 
\end{equation}
Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
\begin{equation}
1 - 0 
\end{equation}

We are going to study the following:
\begin{equation}
1 
\end{equation}
Trivially, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

The following is worth a closer look:
\begin{equation}
x ^{2 } 
\end{equation}
It can be easily proved, that the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

One shall regard the object in question with utmost interest:
\begin{equation}
2 \cdot x 
\end{equation}
Unsurprisingly, the derivative of this is equal to
\begin{equation}
0 \cdot x + 2 \cdot 1 
\end{equation}

@@

The following is worth a closer look:
\begin{equation}
x ^{2 } 
\end{equation}
It can be easily proved, that the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

We will take a closer look at this:
\begin{equation}
2 
\end{equation}
It can be easily proved, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We will take a closer look at this:
\begin{equation}
1 
\end{equation}
It can be easily proved, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

One shall regard the object in question with utmost interest:
\begin{equation}
x ^{2 } 
\end{equation}
As you can see, the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

One shall regard the object in question with utmost interest:
\begin{equation}
1 
\end{equation}
It can be easily proved, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

The following is worth a closer look:
\begin{equation}
x - 2 
\end{equation}
Clearly, the derivative of this is equal to
\begin{equation}
1 - 0 
\end{equation}

Consider the following:
\begin{equation}
1 
\end{equation}
Obviously, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We shall ponder the following:
\begin{equation}
x ^{2 } 
\end{equation}
Unsurprisingly, the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

We are going to study the following:
\begin{equation}
1 
\end{equation}
As you can see, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We will take a closer look at this:
\begin{equation}
x ^{2 } 
\end{equation}
Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
\begin{equation}
2 \cdot x 
\end{equation}
Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
\begin{equation}
0 \cdot x + 2 \cdot 1 
\end{equation}

We shall ponder the following:
\begin{equation}
1 
\end{equation}
Obviously, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

One shall regard the object in question with utmost interest:
\begin{equation}
2 
\end{equation}
Trivially, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

The following is worth a closer look:
\begin{equation}
1 
\end{equation}
Trivially, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
\begin{equation}
1 
\end{equation}
As you can see, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

The object of our ultimate interest is the following:
\begin{equation}
x ^{2 } 
\end{equation}
Unsurprisingly, the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

The object of our ultimate interest is the following:
\begin{equation}
1 
\end{equation}
Obviously, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
\begin{equation}
1 
\end{equation}
Clearly, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We shall ponder the following:
\begin{equation}
x - 2 
\end{equation}
Unsurprisingly, the derivative of this is equal to
\begin{equation}
1 - 0 
\end{equation}

We shall ponder the following:
\begin{equation}
1 
\end{equation}
Clearly, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We shall ponder the following:
\begin{equation}
x ^{2 } 
\end{equation}
It can be easily proved, that the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

We shall ponder the following:
\begin{equation}
1 
\end{equation}
It is now obvious, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

The object of our ultimate interest is the following:
\begin{equation}
x ^{2 } 
\end{equation}
As you can see, the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

The following is worth a closer look:
\begin{equation}
x - 2 
\end{equation}
Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
\begin{equation}
1 - 0 
\end{equation}

One shall regard the object in question with utmost interest:
\begin{equation}
x + 1 
\end{equation}
Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
\begin{equation}
1 + 0 
\end{equation}

We are going to study the following:
\begin{equation}
2 
\end{equation}
It is now obvious, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

Let us take a look at this:
\begin{equation}
\sin x 
\end{equation}
Unsurprisingly, the derivative of this is equal to
\begin{equation}
\cos x \cdot 1 
\end{equation}

We shall ponder the following:
\begin{equation}
x ^{2 } 
\end{equation}
As you can see, the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
\begin{equation}
2 \cdot x 
\end{equation}
Obviously, the derivative of this is equal to
\begin{equation}
0 \cdot x + 2 \cdot 1 
\end{equation}

Let us take a look at this:
\begin{equation}
1 
\end{equation}
As you can see, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

One shall regard the object in question with utmost interest:
\begin{equation}
x ^{2 } 
\end{equation}
Trivially, the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
\begin{equation}
2 
\end{equation}
Trivially, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

Let us take a look at this:
\begin{equation}
1 
\end{equation}
Obviously, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

One shall regard the object in question with utmost interest:
\begin{equation}
1 
\end{equation}
Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

The following is worth a closer look:
\begin{equation}
x ^{2 } 
\end{equation}
As you can see, the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

One shall regard the object in question with utmost interest:
\begin{equation}
1 
\end{equation}
Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
\begin{equation}
1 
\end{equation}
Obviously, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

The object of our ultimate interest is the following:
\begin{equation}
x - 2 
\end{equation}
Obviously, the derivative of this is equal to
\begin{equation}
1 - 0 
\end{equation}

Consider the following:
\begin{equation}
1 
\end{equation}
Trivially, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

One shall regard the object in question with utmost interest:
\begin{equation}
x ^{2 } 
\end{equation}
As you can see, the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

Consider the following:
\begin{equation}
1 
\end{equation}
Obviously, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We are going to study the following:
\begin{equation}
x ^{2 } 
\end{equation}
It can be easily proved, that the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

One shall regard the object in question with utmost interest:
\begin{equation}
x - 2 
\end{equation}
Obviously, the derivative of this is equal to
\begin{equation}
1 - 0 
\end{equation}

The following is worth a closer look:
\begin{equation}
1 
\end{equation}
As you can see, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We are going to study the following:
\begin{equation}
2 
\end{equation}
Unsurprisingly, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We shall ponder the following:
\begin{equation}
\sin x 
\end{equation}
It is now obvious, that the derivative of this is equal to
\begin{equation}
\cos x \cdot 1 
\end{equation}

The following is worth a closer look:
\begin{equation}
x + 1 
\end{equation}
Unsurprisingly, the derivative of this is equal to
\begin{equation}
1 + 0 
\end{equation}

One shall regard the object in question with utmost interest:
\begin{equation}
4 
\end{equation}
It is now obvious, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

Consider the following:
\begin{equation}
2 
\end{equation}
Clearly, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

Let us take a look at this:
\begin{equation}
\cos x 
\end{equation}
Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
\begin{equation}
-\sin x \cdot 1 
\end{equation}

We will take a closer look at this:
\begin{equation}
x + 1 
\end{equation}
It is now obvious, that the derivative of this is equal to
\begin{equation}
1 + 0 
\end{equation}

One shall regard the object in question with utmost interest:
\begin{equation}
2 
\end{equation}
It can be easily proved, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
\begin{equation}
\sin x 
\end{equation}
Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
\begin{equation}
\cos x \cdot 1 
\end{equation}

Consider the following:
\begin{equation}
1 
\end{equation}
It is now obvious, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

Consider the following:
\begin{equation}
x ^{2 } 
\end{equation}
Clearly, the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

Let us take a look at this:
\begin{equation}
2 \cdot x 
\end{equation}
It is now obvious, that the derivative of this is equal to
\begin{equation}
0 \cdot x + 2 \cdot 1 
\end{equation}

We shall ponder the following:
\begin{equation}
1 
\end{equation}
Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We shall ponder the following:
\begin{equation}
x ^{2 } 
\end{equation}
Unsurprisingly, the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

Let us take a look at this:
\begin{equation}
2 
\end{equation}
Obviously, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

One shall regard the object in question with utmost interest:
\begin{equation}
1 
\end{equation}
It is now obvious, that the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We shall ponder the following:
\begin{equation}
1 
\end{equation}
Obviously, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

The following is worth a closer look:
\begin{equation}
1 
\end{equation}
Obviously, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

The following is worth a closer look:
\begin{equation}
1 
\end{equation}
Trivially, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

The object of our ultimate interest is the following:
\begin{equation}
x - 2 
\end{equation}
Unsurprisingly, the derivative of this is equal to
\begin{equation}
1 - 0 
\end{equation}

The object of our ultimate interest is the following:
\begin{equation}
1 
\end{equation}
Obviously, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

Consider the following:
\begin{equation}
x ^{2 } 
\end{equation}
It can be easily proved, that the derivative of this is equal to
\begin{equation}
2 \cdot x ^{2 - 1 } \cdot 1 
\end{equation}

We shall ponder the following:
\begin{equation}
1 
\end{equation}
Trivially, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

We shall ponder the following:
\begin{equation}
x - 2 
\end{equation}
Clearly, the derivative of this is equal to
\begin{equation}
1 - 0 
\end{equation}

We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
\begin{equation}
x + 1 
\end{equation}
As you can see, the derivative of this is equal to
\begin{equation}
1 + 0 
\end{equation}

We will take a closer look at this:
\begin{equation}
1 
\end{equation}
Obviously, the derivative of this is equal to
\begin{equation}
0 
\end{equation}

>>>>

We will take a closer look at this:
\begin{equation}
\sin x 
\end{equation}
Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
\begin{equation}
\cos x \cdot 1 
\end{equation}

@@

\newpage
\section{Taylor series}
Let us find the Taylor series at $x = 5$ of the following function:
\begin{equation}
\left( x + 1 \right) ^{\frac{\sin x }{2 } } \cdot \left( \arctan \sqrt {x ^{2 } + 1 } \right) ^{x - 2 } 
\end{equation}

We will allow ourselves to divert the reader's attention to this gem of mathematical wonder:
\begin{equation}
\sin x 
\end{equation}
It is now obvious, that the derivative of this is equal to
\begin{equation}
\cos x \cdot 1 
\end{equation}

@@

@@

One shall regard the object in question with utmost interest:
\begin{equation}
x - 2 
\end{equation}
Any self-respecting mathematician would find it obvious, that the derivative of this is equal to
\begin{equation}
1 - 0 
\end{equation}

@@

Consider the following:
\begin{equation}
x - 2 
\end{equation}
As you can see, the derivative of this is equal to
\begin{equation}
1 - 0 
\end{equation}

@@
